### 2016-01-20 paper.tex
Make first sentence of conclusion its own paragraph as suggested by @nearyvs

The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
turbine was measured in a towing tank. Performance was assessed for Reynolds
number dependence, showing a convergence to a weakly $Re$-dependent linear
regime at approximately $Re_D \approx 1 \times 10^6$ or $Re_{c,\mathrm{ave}}
\approx 2 \times 10^5$. Comparison was made between this turbine and the higher
solidity UNH-RVAT, tested in nearly identical conditions, which showed similar
Reynold number thresholds but a flatter linear regime, likely to due virtual
camber of the higher chord-to-radius ratio of the UNH-RVAT blades.

>>>>

The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
turbine was measured in a towing tank.

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynold number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades.
